---
title: "State_to_live app"
author: "Nadia Stavisky"
date: "October 17, 2019"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      tidy = TRUE,
                      tidy.opts = list(width.cutoff = 60))
#load libraries
library(tidyr)
library(dplyr)
library(ggplot2)
library(plotly)
library(knitr)
```

## Intorduction
This [app](http://rpubs.com/NadiaStavisky/540387) allows users to chose US States based on their climat preferences:
- How many days in a year you are willing to freeze?
- How many States you would like to consider from?
- Would you like to consider other details such as population, life expectancy etc.?

## Recources
Data set used for application: state.x77.
state.x77 - matrix with 50 rows and 8 columns giving the following statistics in the respective columns:
- **Population:** population estimate as of July 1, 1975
- **Income:** per capita income (1974)
- **Illiteracy:** illiteracy (1970, percent of population)
- **Life Exp:** life expectancy in years (1969-71)
- **Murder:** murder and non-negligent manslaughter rate per 100,000 population (1976)
- **HS Grad:** percent high-school graduates (1970)
- **Frost:** mean number of days with minimum temperature below freezing (1931-1960) in capital or large city
- **Area:**  land area in square miles
Source
U.S. Department of Commerce, Bureau of the Census (1977) Statistical Abstract of the United States.
U.S. Department of Commerce, Bureau of the Census (1977) County and City Data Book.

## Instructions
### Filters
1. Mean number of days with minimum temperature below freezing (1931-1960)
Summary of number of days below freezing accross all States
```{r data processing, echo = FALSE}
#set up dtat set
State <- state.abb
state_data <- as.data.frame(cbind(state.abb,state.x77))
num_col <- c("Population", "Income", "Illiteracy", "Life Exp", "Murder", "HS Grad", "Frost", "Area")
state_data[num_col] <- sapply(sapply(state_data[num_col],as.character), as.numeric)
summary(state_data$Frost)
```

2. Number of Top warmest states (1-50)
Number of states in the data set:
```{r states_num}
dim(state_data)[1]
```

## Plot
Map plot shows selected States based on applied filters 
(example below shows States that on average have maximum 25 freezing days within a year):
```{r map}
borders <- list(color = toRGB("red"))
map_options <- list(
            scope = 'usa',
            projection = list(type = 'albers usa'),
            showlakes = TRUE,
            lakecolor = toRGB("white")
        )
map_data <- state_data %>%
    filter(Frost >= 0 & Frost <= 25)
plot_ly(data = map_data, z = map_data$Frost, locations = map_data$state.abb,
                type = 'choropleth', locationmode = 'USA-states',
                color = map_data$Frost, colors = 'Spectral', marker = list(line = borders)) %>%
            layout(geo = map_options)

```


## Table
Table provides Statistical details of the US States:
```{r table}
kable(map_data, format = "pandoc")

```


## What State did you chose?





